Real Time Shape Reconstruction for Near Earth Asteroid Landing

### 2018-03-31 abstract.tex
Add more introduction

 % Types of missions near asteroids (impact mitigation, mining, science)

>>>>

Another key dynamic consideration is the coupling between rotational and translational states around the asteroid.
The coupling is induced due to the different gravitational forces experienced on various portions of the spacecraft. 
The effect of the gravitational coupling is related to the ratio of the spacecraft size and orbital radius~\cite{hughes2004}.
For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
References~\cite{elmasri2005} and~\cite{sanyal2004a} investigated the copuling of an elastic dumbbell spacecraft in orbit about a central body, but only considered teh case of a spherically symmetric central body.
Furthermore, the spacecraft model is assumed to remain in a planar orbit.
As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
Reference~\cite{misra2015b}
 % Types of missions near asteroids (impact mitigation, mining, science)
